The Astropy Project

### 2017-11-10 main.tex
subpackage

\section*{Global TODO items}
\begin{itemize}
    \item subpackage vs sub-package need to be standardized throughout the paper
    \item spell check!
\end{itemize}

@@

		The \package{astropy.io.ascii} sub-package now provides the capability
		to read a table within an HTML file or web URL into an astropy
		\texttt{Table} object. This requires the \package{BeautifulSoup4}
		package to be installed.  Conversely a \texttt{Table} object can now
		be written out as an HTML table.

@@

		The \package{astropy.io.fits} sub-package now provides a command line
		script for inspecting the header(s) of a FITS file.  Running
		\texttt{fitsheader file.fits} in a terminal prints the header
		information to the screen in a human-readable format. Run
		\texttt{fitsheader --help} to see the full usage documentation.

@@

		The \package{astropy.io.fits} sub-package now supports \emph{lazy
		loading}, where all HDUs are not loaded until they are requested (or
		the file is closed). This should provide substantial speedups for
		situations using the convenience functions (e.g., \texttt{getheader()}
		or \texttt{getdata()}) to get HDU’s that are near the front of a file
		with many HDU’s.

>>>>

\section*{Global TODO items}
\begin{itemize}
    \item subpackage not sub-package!
    \item spell check!
\end{itemize}

@@

		The \package{astropy.io.ascii} subpackage now provides the capability
		to read a table within an HTML file or web URL into an astropy
		\texttt{Table} object. This requires the \package{BeautifulSoup4}
		package to be installed.  Conversely a \texttt{Table} object can now
		be written out as an HTML table.

@@

		The \package{astropy.io.fits} subpackage now provides a command line
		script for inspecting the header(s) of a FITS file.  Running
		\texttt{fitsheader file.fits} in a terminal prints the header
		information to the screen in a human-readable format. Run
		\texttt{fitsheader --help} to see the full usage documentation.

@@

		The \package{astropy.io.fits} subpackage now supports \emph{lazy
		loading}, where all HDUs are not loaded until they are requested (or
		the file is closed). This should provide substantial speedups for
		situations using the convenience functions (e.g., \texttt{getheader()}
		or \texttt{getdata()}) to get HDU’s that are near the front of a file
		with many HDU’s.
